### 2023-03-13 paper.tex
Write about attention masking

\documentclass[twoside]{article}
\usepackage{seminarpaper}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{csquotes}
\usepackage{tikz}

@@

@@

@@

\subsection{Toolformer}
Transformers are able to produce very natural text but as previously mentioned, they struggle with seemingly
simple tasks such as simple mathematical calculations and factual information gathering.
To get around of these limitations, transformers can be taught to use external tools
to offload these tasks to applications better suited to them. \cite{schick_toolformer_2023} 
This can be achieved using additional fine tuning, as is the case with Toolformer
\cite{schick_toolformer_2023}, or by using few-shot methods telling the model 
about the tools available to it, as in Toolformer Zero \cite{markus_toolformer_2023}.

>>>>

\documentclass[twoside]{article}
\usepackage[english]{babel}
\usepackage{seminarpaper}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{csquotes}
\usepackage{tikz}

@@

\subsection{Attention masking}

TODO: explain how attention masking works

TODO: explain sparse transformer, used in gpt-3 (maybe 2 also)

The original transformer's encoder-decoder architecture as specified in 
\cite{vaswani_attention_2017} corresponds to the leftmost masking pattern as
specified in \ref{masking_patterns}. T5 uses this architecture and masking pattern
\cite{raffel_exploring_2020}. As previously mentioned, BERT uses an encoder
only architecture \cite{devlin_bert_2019} and uses a fully-visible masking 
pattern with a special classification token \cite{raffel_exploring_2020}. GPT on
the other hand, uses a decoder only architecture \cite{radford_improving_nodate}
and uses causal masking \cite{liu_generating_2018}.

Prefix masking can be useful for example when translating. The prefix allows the
model to attend to the entire source language sentence and causal masking can be 
used only for the target language sentence prediction. \cite{raffel_exploring_2020}

\begin{figure}[h]
  \centering
  \includegraphics*[scale=0.15]{img/attention_masking.png}
  \caption{
    Different attention masking patterns seen in transformer based language models.
    Dark squares indicate that the attention mechanism can see the input $i$ at time $j$.
    Light squares indicate that the access is blocked for a given pair $i$, $j$. 
    \cite{raffel_exploring_2020}
  }
\end{figure}
\begin{figure}[h]
  \centering
  \includegraphics*[scale=0.15]{img/lm_masking.png}
  \caption{
    Different masking patterns used within language models. Dark lines correspond to 
    fully-visible masking. Light gray lines indicate causal masking.
    \cite{raffel_exploring_2020}
  }
\end{figure}
\label{masking_patterns}

TODO: remake, text not visible
\begin{figure}[h]
  \centering
  \includegraphics*[scale=0.1]{img/sparse_transformer.png}
  \caption{
    \cite{child_generating_2019}
  }
\end{figure}

@@

TODO: talk about GPT sparse transformer, used in gpt-3

@@

\subsection{Toolformer}
Transformers are able to produce very natural text but as previously mentioned, they struggle with seemingly
simple tasks such as simple mathematical calculations and factual information gathering.
To get around of these limitations, transformers can be taught to use external tools
to offload these tasks to applications better suited to them. \cite{schick_toolformer_2023} 
This can be achieved using additional fine tuning, as is the case with Toolformer
\cite{schick_toolformer_2023}, or by using few-shot methods telling the model 
about the tools available to it, as in Toolformer Zero \cite{minosvasilias_markus_toolformer_2023}.
